Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-07-05 manuscript/manuscript.tex
comment on paper structure

The paper is organized as follows:
Section~\ref{sec:data} offers a brief review of the history of the 311
system and the long-term trends presented via a 10-year analysis.
Section~\ref{sec:issues} offers a 
general discussion of data cleansing issues impacting data 
quality and curation efficiency. Section~\ref{sec:structural} examines
the technical dimensions of the dataset, the structural issues. 
In Section~\ref{sec:datatypes} we examine the data fields for compliance 
with the Data Dictionary. Section~\ref{sec:blanks} looks at the 
data fields as regards missing, blank, or N/A entries. Section~\ref{sec:domain} 
explores how data fields comply with a domain of legal 
or acceptable values. Section~\ref{sec:inconsistencies} deals 
with the important issues surrounding logical inconsistencies 
and concerning patterns in the data. Section~\ref{sec:precision} 
explores the issue of precision versus accuracy. Section~\ref{sec:duplicates}
identifies duplicate and redundant data fields. Section~\ref{sec:improvements} provides 
actionable suggestions for mitigating or resolving identified issues. 
Following this, Section~\ref{sec:protocol} outlines a series of general 
principles for the release of open data, drawing from our findings. The 
paper concludes with a discussion and recommendations in 
Section~\ref{sec:discussion}, encapsulating the key insights and 
implications of our research.

>>>>

The paper is organized as follows:
Section~\ref{sec:data} offers a brief review of the history of the 311
system and the long-term trends presented via a 10-year analysis.
Section~\ref{sec:issues} offers a 
general discussion of data cleansing issues impacting data 
quality and curation efficiency. Section~\ref{sec:structural} examines
\jy{How about putting all these sections into one section on cass
  study? They can be subsections in the merged section.
  After that, we can have a section on recommendations for open
  data curation based on what we learn from the case study. For each
  recommended principle, we can link to the specifics of the case
  study.}
the technical dimensions of the dataset, the structural issues. 
In Section~\ref{sec:datatypes} we examine the data fields for compliance 
with the Data Dictionary. Section~\ref{sec:blanks} looks at the 
data fields as regards missing, blank, or N/A entries. Section~\ref{sec:domain} 
explores how data fields comply with a domain of legal 
or acceptable values. Section~\ref{sec:inconsistencies} deals 
with the important issues surrounding logical inconsistencies 
and concerning patterns in the data. Section~\ref{sec:precision} 
explores the issue of precision versus accuracy. Section~\ref{sec:duplicates}
identifies duplicate and redundant data fields. Section~\ref{sec:improvements} provides 
actionable suggestions for mitigating or resolving identified issues. 
Following this, Section~\ref{sec:protocol} outlines a series of general 
principles for the release of open data, drawing from our findings. The 
paper concludes with a discussion and recommendations in 
Section~\ref{sec:discussion}, encapsulating the key insights and 
implications of our research.
